Is the direction of Granger causal influence the same as the direction of information flow?

### 2015-07-07 paper.tex
Add GC comparison figure.

In order to determine the direction of causal influence, the Granger Causality metric (ratio of residual variances) from $\{X\}$ to $\{Y\}$ is \emph{compared} to that from $\{Y\}$ to $\{X\}$. The direction of causal influence is taken to be the direction with a greater Granger Causality metric. Further, this direction of causal influence is interpreted to be the direction of information flow -- the interpretation we question in this paper. We also note that many of these works use a spectral version of Granger Causality, that supplies this metric as a function of frequency. It then becomes possible to also determine the brain wave frequency at which these influences occur. However, we restrict our analysis to the simpler non-spectral version of Granger Causality, since it is sufficient to for the purpose of our arguments.

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.2in]{gc-comparison}
	\caption{In order to determine the direction of greater causal influence, the Granger Causality metrics in the forward and reverse directions are compared}
	\label{fig:sk-block-diagram}
\end{figure}

In order to determine the direction of greater causal influence, the Granger Causality metric (ratio of residual variances) from $\{X\}$ to $\{Y\}$ is \emph{compared} to that from $\{Y\}$ to $\{X\}$. The direction of causal influence is taken to be the direction with a greater Granger Causality metric. Further, this direction of causal influence is interpreted to be the direction of information flow -- the interpretation we question in this paper. We also note that many of these works use a spectral version of Granger Causality, that supplies this metric as a function of frequency. It then becomes possible to also determine the brain wave frequency at which these influences occur. However, we restrict our analysis to the simpler non-spectral version of Granger Causality, since it is sufficient to for the purpose of our arguments.
